Determining multi-scale controls on river temperature: a time series approach

### 2017-04-10 manuscript/manuscript.tex
made some plot adjustments

@@

\begin{center}
% \resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/03_fits.pdf}}
\includepdf[pages={1-},scale=0.75]{figures/diagnostic_plots/03_fits.pdf}
\end{center}
\textbf{Figure A3} Model fits (green line = overall fit; blue line = trends-only fit, points = data).

@@

>>>>

%add to appendix A: trends and loadings from 2-trend model

@@

\begin{center}
% \resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/03_fits.pdf}}
\includepdf[pages={1-},scale=0.75]{figures/diagnostic_plots/03_fits.pdf}
\end{center}
\textbf{Figure A3} Model fits (gray line = overall fit; green line = trends-only fit, points = data).

@@

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/01_trends_simple.pdf}}
\end{center}
\textbf{Figure A6} Shared trends from simplified model (no seasonal fixed factor, no snowmelt predictor)

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/02_loadings_simple.pdf}}
\end{center}
\textbf{Figure A7} Factor loadings from simplified model (no seasonal fixed factor, no snowmelt predictor)
